---
title: "Prepare_features"
author: "Javad Khataei"
date: "7/5/2019"
output: html_document
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose of this code
In this code, we work with the dataset created by joining the Ethica and Jaeger files.

- First, we trim the activity column and remove the numbers from it
- Second, we consider the Activity as our outcome so we remove all the Jaeger data but the trimmed activity
- Third, we create three different scenarios
  1. In the first one, the wear location is the outcome and we don't consider the activity type
  2. For the second one, only the activity type is the outcome and we don't consider the wear location
  3. For the third one, we have 18 different classes and we consider both activity type and wear location

### Read the data
```{r message=FALSE, warning=FALSE}
# load the libraries
library(tidyverse)
library(data.table)
library(lubridate)
library(tm)

# set your working directory and read the file
complete_df <<- fread("Ethica_jaeger_merged_metadata_total.csv")
```

### Trim the activity
```{r}
# remove whitespace, then numbers
complete_df <- complete_df$activity %>%
  trimws() %>%
  removeWords(c("1-", "2-" , "3-", "4-" , "5-" , "6-" , "7-" , "8-" , "9-")) %>%
  mutate(complete_df, activity_trimmed = .)
```



### The wear location is the only outcome
```{r}
# use this to model wear location
df_wear <<-
  complete_df %>% select(
    record_time,
    participant_id,
    x_axis,
    y_axis,
    z_axis,
    height,
    weight,
    age,
    gender,
    wear_location
  )
```

### The trimmed activity is the only outcome
```{r}
# use this to model type of activity
df_activity <<-
  complete_df %>% select(
    record_time,
    participant_id,
    x_axis,
    y_axis,
    z_axis,
    height,
    weight,
    age,
    gender,
    activity_trimmed
  )
```

### Both the activity and the wear location are outcomes
Here we have 21 different labels
```{r}
# use this to model both wear location and activity
df_aw <<-
  complete_df %>% select(
    record_time,
    participant_id,
    x_axis,
    y_axis,
    z_axis,
    height,
    weight,
    age,
    gender,
    wear_location,
    activity_trimmed
  ) %>% 
  filter(., !is.na(complete_df$x_axis)) 

df_aw <<- df_aw %>% 
  add_column(.,wear_activity = paste0(df_aw$wear_location,"/",df_aw$activity_trimmed))


df_aw$wear_activity <- str_replace_all(df_aw$wear_activity, " ", "_")

```

