---
title: "Case 4 with 30Hz frequency - Leakage fixed"
author: "Javad Khataei"
date: "8/29/2019"
output:
    html_document:
        code_folding : hide
        toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE , eval = T)
```

## Linear imputation, Counts(x,y,z,vec_mag) and its features

In this markdown, we use the linear imputed data. Only **Counts(x,y,z,vec_mag) and its features** variables are used for this model. We can apply the following models using the `ApplyModels` function from `BEAP` package:

- `RF`, Random Forest
- `LDA`, Linear Discriminant Analysis
- `NB`, Naive Bayes
- `SVM`, Support Vector Machines
- `KNN`, k-Nearest Neighbors
- `DT`, desicion Tree

 
## Read and prepare the data
```{r message=FALSE, warning=FALSE}

#import libraries
library(data.table)
library(tidyverse)
library(lubridate)
library(activityCounts)
library(magrittr)
library(scales)
library(caret)
library(stringr)
library(MLmetrics)
library(PRROC)
library(gridExtra)
library(kableExtra)
library(imputeTS)
library(Beap) # It's not on CRAN yet





# ---------------------------- Read the data ----------------------

# set the working directory to the folder that has the raw data and the intervals file
OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  main_path <-
    "Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data"
} else {
  main_path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/studies/smarphone_accel/data"
}
# Read the file with x,y,z axis and labels.
Ethica_df <-
  fread(paste0(main_path,"/Ethica_Jaeger_Merged/pocket/pocket_with_couns_and_vec_meg_30Hz.csv"))


# ---------------------------- Prepare the data ----------------------------

# Only participant 112 is  not properly classified
working_df  <-
  Ethica_df %>% filter(!(participant_id %in% c(112)))


working_df %<>%  dplyr::select(c(x, y, z, trimmed_activity))
working_df  %<>% filter(trimmed_activity != "transit")


# models canot work with strin
working_df$trimmed_activity  %<>% str_replace_all(" ", "_") %>%
  factor(
    levels = c(
      "Lying",
      "Sitting",
      "Self_Pace_walk",
      "Running_3_METs",
      "Running_5_METs",
      "Running_7_METs"
    )
  )

# Removing NAs reduces the freq from 30Hz to 1Hz

working_df  %<>% na.omit()

```

Note that we need to exclude Participant number 112  as it is not properly classified. 

# Add new features
As the *counts* are calculated for each second, using a window of 5 means that we are generating the feature for 10 second period.

```{r message= T , warning=FALSE}
frequency <- 1
window_size_sec <- 5
# The number of features reduces by this
reduction_coef <-  window_size_sec * frequency
new_features_df <-
  GenerateFeatures(raw_df = working_df,
                   window_size_sec = window_size_sec,
                   frequency = frequency)

# Increase the frequency
new_features_df <-
  new_features_df[rep(1:nrow(new_features_df) , each = reduction_coef),]


# reduce the size of working_df to add new_features
working_df  %<>% slice(1:nrow(new_features_df))
##  
working_df <- bind_cols(working_df, new_features_df)
# some models cannpt train if there is any NA
working_df  %<>% na_interpolation(option =  "linear")

```
# Fixing the high accuracy issue
Since we have a dataset with 58 predictive features and 55 of these features are constant for every 30 readings, we have a leaky training set. The window is five second, and the frequency is 1Hz. Therefore every 5 readings have the same features. To fix this issue, we only use the first observation in each window. Also, the size of the dataset will be smaller, and the modelling process will be faster. 


```{r}

freq <- reduction_coef

working_df  %<>% groupdata2::group(n = freq, method = "greedy") %>%
  rename( "id" = .groups )

working_df  %<>% group_by(id) %>%
  summarise_all(first) %>% 
  select(-id)

```


## Apply models
```{r message=TRUE, warning=FALSE}
results <-
    Beap::ApplyModels(
        working_df = working_df,
        model_names = c("RF"), #c("RF", "LDA", "NB", "SVM", "KNN", "DT")
        split_ratio = 0.7,
        shrink = 1,
        return_plots = TRUE,
        save_results = FALSE,
        min_node_size = 5
        
    )
```



## Compare the results


```{r message=FALSE, warning=FALSE}
print(results$Plots)

results$`Model-Accuracy` %>%  
  select(Accuracy, AUC, prAUC, Mean_F1, Mean_Sensitivity, Mean_Specificity) %>% 
  round(digits = 4) %>% 
    kable(label = " Accuracy for each model") %>%
    kable_styling(full_width = T, bootstrap_options = c("striped", "hover"))
 

#save(results, "Case3_reults.RData")
```

### Feature importance for RF

```{r}


imp_table <- results$RF_Feature_Importance$importance

row_names <- rownames(imp_table)

imp_table  %>% data.frame(row_names, .) %>% 
  arrange(desc(Overall) ) %>% 
  kable(label = " Top ten important features for RF model") %>%
    kable_styling(full_width = T, bootstrap_options = c("striped", "hover"))

```

