---
title: "Case 1 30Hz "
author: "Javad Khataei"
date: "9/13/2019"
output:
    html_document:
        code_folding : hide
        toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Linear imputation, X, Y, Z axis

In this markdown, we use the linear imputed data. Only **X, Y, and Z-axis** variables are used for this model. We can apply the following models using the `ApplyModels` function from `BEAP` package:

- `RF`, Random Forest
- `LDA`, Linear Discriminant Analysis
- `NB`, Naive Bayes
- `SVM`, Support Vector Machines
- `KNN`, k-Nearest Neighbors
- `DT`, desicion Tree

 
## Read and prepare the data
```{r message=FALSE, warning=FALSE}

#import libraries
library(data.table)
library(tidyverse)
library(lubridate)
library(activityCounts)
library(magrittr)
library(scales)
library(caret)
library(stringr)
library(MLmetrics)
library(PRROC)
library(gridExtra)
library(kableExtra)
library(Beap) # It's not on CRAN yet





# ---------------------------- Read the data ----------------------

# set the working directory to the folder that has the raw data and the intervals file
OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  main_path <-
    "Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data"
} else {
  main_path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/studies/smarphone_accel/data"
}

# Read the file with x,y,z axis and labels.
Ethica_df <-
  fread(paste0(main_path,"/Ethica_Jaeger_Merged/pocket/pocket_with_couns_and_vec_meg_30Hz.csv"))


# ---------------------------- Prepare the data ----------------------------

# Only participant 112 is  not properly classified
working_df  <-
  Ethica_df %>% filter(!(participant_id %in% c(112)))

# Model A_1 only uses raw accel data
working_df %<>%  dplyr::select(c(x_axis, y_axis, z_axis, trimmed_activity))
working_df  %<>% filter(trimmed_activity != "transit")


# models canot work with strin
working_df$trimmed_activity  %<>% str_replace_all(" ", "_") %>%
  factor(
    levels = c(
      "Lying",
      "Sitting",
      "Self_Pace_walk",
      "Running_3_METs",
      "Running_5_METs",
      "Running_7_METs"
    )
  )


```

Note that we need to exclude Participant number 112 as it is not properly classified. 



## Apply models
```{r message=TRUE, warning=FALSE}
results <-
    Beap::ApplyModels(
        working_df = working_df,
        model_names =c("RF","LDA", "NB"), #c("RF", "LDA", "NB", "SVM", "KNN", "DT")
        split_ratio = 0.7,
        shrink = 1,
        return_plots = TRUE,
        save_results = FALSE
    )
```



## Compare the results


```{r message=FALSE, warning=FALSE}
print(results$Plots)

results$`Model-Accuracy` %>%  
  select(Accuracy, AUC, prAUC, Mean_F1, Mean_Sensitivity, Mean_Specificity) %>% 
  round(digits = 3) %>% 
    kable(label = " Accuracy for each model") %>%
    kable_styling(full_width = T, bootstrap_options = c("striped", "hover"))
    
#save(results, file = "Case1_results.RData")
```

