---
title: "Combine Ethica data"
author: "Javad Khataei"
date: "7/11/2019"
output:
   html_document:
     code_folding : hide
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**For 10Hz Run The First Chunck. For 30Hz Run The Second Chunck**

### Summary:
This file reads  Ethica files for each participant and different wear locations. Then it imputed the gaps of the accelerometer data, and finally, it binds them together to have a single dataset.

### Steps:

1. Create file names, for example: "/108/108_hand.csv."
2. Read the files and create a longer dataset for each that doesn't have the gap.
The start and the end time of the longer dataset are the same as each file, but there is no gap.
3. Join the two datasets and impute numeric values with the interpolation method
4. Impute the wear locations
5. Repeat this for all files and bind them
6. Save the results into "Ethica_imputed_combined.csv"

## 10 Hz calculations
#### Run this chunk
```{r eval= FALSE}

#import libraries
library(data.table)
library(tidyverse)
library(lubridate)
library(scales)
library(activityCounts)
library(imputeTS)


##-------------------------------------The root folder---------------------------------##
# set the working directory to the folder that has the raw data and the intervals file
OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  main_path <-
    "Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/Ethica"
} else {
  main_path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/studies/smarphone_accel/data/Ethica"
}
setwd(dir = main_path)


#read intervals file to get the participants ids
participant_list <- fread("intervals.csv")

# for participants 100 to 107, 110, 135, and 148 there is no Jaeger data. Also, Ethica data is not available in 2018
# so use participats 108, 109 , 111 to 159


participant_list <-
  participant_list %>%  na.omit() %>% slice((9:59)) %>% slice(c(-3,-28,-41)) %>% select(userid)

# create a list of possible wear locations
wear_locations <- c("hand", "back", "pock")

# create a dataset to store all the final data
final_df <- NULL

# Read Ethica files, impute each one of them, and then bind them
participant_list$userid %>% map(function(participant_id) {
  wear_locations %>%  map(function(wear_loc) {
    # create Ethica file name a based on wear_loc and participant_id
    Ethica_file_name <<-
      paste0(participant_id, "/", participant_id, "_", wear_loc, ".csv")
    
    # read and convert to datetime
    working_df <- fread(Ethica_file_name)
    working_df$record_time <-
      working_df$record_time %>% as_datetime()
    
    ##---------status---------------#
    print(paste0(Ethica_file_name," is read"))
    
    ## Create a dataframe with the same staring and end point as the data
    longer_df <-
      seq(
        first(working_df$record_time),
        last(working_df$record_time),
        by = period(num = 0.1, units = "second")
      ) %>%  as.data.frame()
    colnames(longer_df) <- "record_time"

    # Join the datasets
    working_df <-
      full_join(longer_df, working_df , by = "record_time")
    
    
    # impute NAs by linear intrapolation
    # na.interapolation  only works with numeric data
    working_df <- working_df %>%
      select(-wear_location) %>%
      na_interpolation()
    
    # add  wear location
    working_df$wear_location <- wear_loc
    
    #order data to solve the prblem with P #111,122, 125, 151
    ##### ========== you can remove it if the problem is solved
    #working_df <- working_df %>% arrange(record_time)

    
    #save for each participant
    fname <- paste0(participant_id,"_",wear_loc,"_imputed.csv")
    fwrite(working_df,file = paste0("Imputed/",fname))


    # bind all the data and store in final_df
    final_df <<- bind_rows(final_df, working_df)
    

    
    ##---------status---------------#
    print(paste0(Ethica_file_name," is added"))
    
  })

})
fwrite(x = final_df,file = "Ethica_imputed_combined.csv")

```

## 30 Hz calculations
For 30Hz calculations we need to run this chunk
```{r 30hz eval= FALSE}

#import libraries
library(data.table)
library(tidyverse)
library(lubridate)
library(scales)
library(activityCounts)
library(imputeTS)
library(magrittr)



##-------------------------------------The root folder---------------------------------##
# set the working directory to the folder that has the raw data and the intervals file
OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  main_path <-
    "Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/Ethica"
} else {
  main_path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/studies/smarphone_accel/data/Ethica"
}
setwd(dir = main_path)


#read intervals file to get the participants ids
participant_list <- fread("intervals.csv")

# for participants 100 to 107, 110, 135, and 148 there is no Jaeger data. Also, Ethica data is not available in 2018
# so use participats 108, 109 , 111 to 159


participant_list <-
  participant_list %>%  na.omit() %>% slice((9:59)) %>% slice(c(-3,-28,-41)) %>% select(userid)

# create a list of possible wear locations
wear_locations <- c( "pock","hand", "back")

# create a dataset to store all the final data
final_df <- NULL

# Read Ethica files, impute each one of them, and then bind them
participant_list$userid %>% map(function(participant_id) {
  wear_locations %>%  map(function(wear_loc) {
    # create Ethica file name a based on wear_loc and participant_id
    Ethica_file_name <<-
      paste0(participant_id, "/", participant_id, "_", wear_loc, "_30Hz.csv")
    
    # read and convert to datetime
    working_df <- fread(Ethica_file_name)
    working_df$record_time <-
      working_df$record_time %>% as_datetime()
    
    ##---------status---------------#
    print(paste0(Ethica_file_name," is read"))
    
    
    ## plot the data to see the gaps
    working_df %>% select(record_time, x_axis) %>% slice(55000:60000) %>%
      ggplot(aes(x = record_time , y = x_axis)) +
      geom_point()
    
    
    
    ## Create a dataframe with the same staring and end point as the data
    longer_df <-
      seq(
        first(working_df$record_time),
        last(working_df$record_time),
        by = period(num = 0.033333333, units = "second")
      ) %>%  as.data.frame()
    colnames(longer_df) <- "record_time"
    
    
    # we need to round to make these datasets equal, 
    # unless they are slightly different and we cannot join them
     working_df$record_time  %<>% round_date(unit = "0.0001s")
     longer_df$record_time  %<>%  round_date(unit = "0.0001s")

    # Join the datasets
    working_df <-
      full_join(longer_df, working_df , by = "record_time")
    
    
    # impute NAs by linear intrapolation
    # na.interapolation  only works with numeric data
    working_df <- working_df %>%
      select(-wear_location) %>%
      na_interpolation()
    
    # add  wear location
    working_df$wear_location <- wear_loc
    
    #order data to solve the prblem with P #111,122, 125, 151
    ##### ========== you can remove it if the problem is solved
    #working_df <- working_df %>% arrange(record_time)

    
    #save for each participant
    fname <- paste0(participant_id,"_",wear_loc,"_imputed.csv")
   # fwrite(working_df,file = paste0("Imputed/",fname))


    # bind all the data and store in final_df
    final_df <<- bind_rows(final_df, working_df)
    

    
    ##---------status---------------#
    print(paste0(Ethica_file_name," is added"))
    
  })

})
fwrite(x = final_df,file = "Ethica_imputed_combined_30Hz.csv")

```



#### Special imputation methos
Here we use the special method from `Beap` package for imutation and we focus only on the pocket loaction.
```{r eval= FALSE}

#import libraries
library(data.table)
library(tidyverse)
library(lubridate)
library(scales)
library(activityCounts)
library(imputeTS)
library(Beap)


##-------------------------------------The root folder---------------------------------##
# set the working directory to the folder that has the raw data and the intervals file
OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  main_path <-
    "Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data/Ethica"
} else {
  main_path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/studies/smarphone_accel/data/Ethica"
}
setwd(dir = main_path)


#read intervals file to get the participants ids
participant_list <- fread("intervals.csv")

# for participants 100 to 107, 110, 135, and 148 there is no Jaeger data. Also, Ethica data is not available in 2018
# so use participats 108, 109 , 111 to 159


participant_list <-
  participant_list %>%  na.omit() %>% slice((9:59)) %>% slice(c(-3,-28,-41)) %>% select(userid)

# create a list of possible wear locations, For now we only use the pocket location
wear_locations <- c("pock")

# create a dataset to store all the final data
final_df <- NULL

# Read Ethica files, impute each one of them, and then bind them
participant_list$userid %>% map(function(participant_id) {
  wear_locations %>%  map(function(wear_loc) {
    # create Ethica file name a based on wear_loc and participant_id
    Ethica_file_name <<-
      paste0(participant_id, "/", participant_id, "_", wear_loc, ".csv")
    
    # read and convert to datetime
    working_df <- fread(Ethica_file_name)
    working_df$record_time <-
      working_df$record_time %>% as_datetime()
    
    ##---------status---------------#
    print(paste0(Ethica_file_name," is read"))
    
    ## Create a dataframe with the same staring and end point as the data
    longer_df <-
      seq(
        first(working_df$record_time),
        last(working_df$record_time),
        by = period(num = 0.1, units = "second")
      ) %>%  as.data.frame()
    colnames(longer_df) <- "record_time"

    # Join the datasets
    working_df <-
      full_join(longer_df, working_df , by = "record_time")
    
    
    # impute NAs by special imputation method fron Beap package
    working_df <- working_df %>%
      Beap::Impute(time_period_length = 40, k = 3)
    

    # #save for each participant
    # fname <- paste0(participant_id,"_",wear_loc,"_imputed.csv")
    # fwrite(working_df,file = paste0("Imputed-Special/",fname))


    # bind all the data and store in final_df
    final_df <<- bind_rows(final_df, working_df)
    

    
    ##---------status---------------#
    print(paste0(Ethica_file_name," is added"))
    
  })

})
fwrite(x = final_df,file = "Ethica_pocket_special_imputed_combined.csv")

```


