---
title: "Model_A_4"
author: "Javad Khataei"
date: "8/16/2019"
output:
    html_document:
        code_folding : hide
        toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Special imputation, Counts,metadata 

In this markdown, we use the Special imputed data. **metada, `counts`** variables are used for this model. We read the CSV file which contains x,y and z `Counts` and can then apply the following models using the `ApplyModels` function from `BEAP` package:

- `RF`, Random Forest
- `LDA`, Linear Discriminant Analysis
- `NB`, Naive Bayes
- `KNN`, k-Nearest Neighbors
- `DT`, desicion Tree

## Read and prepare the data
```{r message=FALSE, warning=FALSE}

#import libraries
library(data.table)
library(tidyverse)
library(lubridate)
library(activityCounts)
library(magrittr)
library(scales)
library(caret)
library(stringr)
library(MLmetrics)
library(PRROC)
library(gridExtra)
library(kableExtra)
library(imputeTS)
library(doParallel)
library(Beap) # It's not on CRAN yet





# ---------------------------- Read the data ----------------------

# set the working directory to the folder that has the raw data and the intervals file
OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  main_path <-
    "Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data"
} else {
  main_path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/studies/smarphone_accel/data"
}

# Read the file with x,y,z axis and labels.
Ethica_df <-
  fread(paste0(main_path,"/Ethica_Jaeger_Merged/pocket/All_participants_pocket_with_count_special_imputation.csv"))


# ---------------------------- Prepare the data ----------------------------

# Participants 112 , 121 .122 , and 132 are not properly classified
working_df  <-
  Ethica_df %>% filter(!(participant_id %in% c(112, 121, 122, 132)))

# Model A_1 only uses raw accel data
working_df %<>%  dplyr::select(c( height, weight, age,gender, x, y, z, trimmed_activity))
working_df  %<>% filter(trimmed_activity != "transit")


# models canot work with strin
working_df$trimmed_activity  %<>% str_replace_all(" ", "_") %>%
  factor(
    levels = c(
      "Lying",
      "Sitting",
      "Self_Pace_walk",
      "Running_3_METs",
      "Running_5_METs",
      "Running_7_METs"
    )
  )
# To reduce the frequency
working_df  %<>% groupdata2::group(n = 30, method = "greedy") %>%
  rename("id" = .groups)
working_df  %<>% group_by(id) %>%
  summarise_all(first) %>%
  select(-id)


```

Note that we need to exclude Participants number 112 , 121 .122 , and 132 as they are not properly classified. Also, to save time, we run the models on some of the data. Check the code for more details.



## Apply models
```{r message=TRUE, warning=FALSE}
results <-
    Beap::ApplyModels(
        working_df = working_df,
        model_names = c("RF"), #c("RF", "LDA", "NB", "SVM", "KNN", "DT")
        split_ratio = 0.7,
        shrink = 1,
        return_plots = TRUE,
        save_results = FALSE
    )


```

## Compare the results



```{r message=FALSE, warning=FALSE}
# Uncomment if need to plot several plot in one image
# p_LDA <- results$Plots["LDA"]$LDA
# p_RF <- results$Plots["RF"]$RF
#grid.arrange(p_LDA, p_RF, ncol=1)
print(results$Plots)

results$`Model-Accuracy` %>%  
  select(Accuracy, AUC, prAUC ) %>% 
    kable(label = " Accuracy for each model") %>%
    kable_styling(full_width = T, bootstrap_options = c("striped", "hover"))
```

