---
title: "How to sync Ethica and Jaeger"
author: "Javad Khataei"
date: "7/17/2019"
output: html_document
---

```{r setup, include=FALSE}
OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  main_path <-
    "Z:/Research/dfuller/Walkabilly/studies/smarphone_accel/data"
} else {
  main_path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/studies/smarphone_accel/data"
}
knitr::opts_chunk$set(echo = TRUE , eval =F)
knitr::opts_knit$set(root.dir= main_path)
```




1. Use Jan, 108 and 1?? Only pocket 75
2. Use 10 min before and after for them according to intervals
So if interval says 10:30 to 11:40 we select 10:20 to 11:50. Still apply 2:30 difference.
3. Use a loop up to 20 it goes
    1. For each loop add 30 sec and create a data set
    2. Merge the data set with Jaeger (No need for combining all the data)
    3. Trim the activity and make it ready for classification. No need for metadata
4. Delete "transit"
5. Optional; Delete 10% from the beginning and the end
6. Calculate Counts
7. Apply a simple model
8. Find the best one and choose that for time adjustment

```{r include=FALSE}
#import packages and read the data

#import libraries
library(data.table)
library(tidyverse)
library(lubridate)
library(scales)
library(activityCounts)
library(imputeTS)
library(caret)
library(magrittr)

main_df <- fread("Ethica_Jaeger_Merged/pocket/pocket.csv")

working_df <- main_df %>% filter(participant_id == 108) %>%  select(record_time,x_axis,y_axis,z_axis,trimmed_activity)

working_df$record_time  %<>% as_datetime()

```



## Create Counts
```{r}
# Change frequency
# Repeat the data three times for each timestep
working_df <- working_df[rep(1:nrow(working_df) , each = 3), ]
start_time <- working_df$record_time %>%  first() %>%  as_datetime()


# Calculate counts
counts <- working_df  %>% counts(data = .,x_axis = 2,y_axis = 3,z_axis = 4,hertz = 30, start_time = start_time)
colnames(counts)[1] <- "record_time"


#Join with the raw data and impute 
working_df  %<>% full_join(.,counts) %>% fill(x, y, z)


# delete transit
working_df  %<>% filter(trimmed_activity != "transit")


#save for Weka
fwrite(working_df,"Ethica_Jaeger_Merged/pocket/108_pocket_counts.csv")

```


## Create a Simple Model
We use Caret to build a linear model for classification:
```{r}





```

